\LARGE \bf Approximately Orchestrated Routing and Transportation Analyzer:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-29 papers/itsc_2012/submitted2.tex
Couple of minor grammatical changes

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation of
the real world in a few minutes. AORTA is available open-source and is easily
extensible\footnote{Code available at
\texttt{http://code.google.com/p/road-rage}}, making it easy for users to test
out a number of agent behaviors and intersection policies in a short time span.

@@

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine \cite{scala}. Scala provides the advantage of functional programming
constructs while still permitting imperative style.  Extensions and clients
built on top of AORTA can be written in either Java or Scala. The software is
open-source and easily extensible. For instance, the stop sign sign policy used
in experiments described in Section \ref{sec:results} is implemented in just 70
lines of code.

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining the
center line that divides the road into two directions of travel. AORTA
interprets these points as straight line segmentss and projects parallel lanes
out using a fixed width. Turns are approximated with a single straight line
segment connecting the end of one lane to the start of another.

@@

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. In some circumstances, one intersection appears
to be several in close proximity, since OSM only has geometric, not functional,
data on how roads meet. If OSM encoded this information, the realism of the
simulation would improve. Other simulators have dealt with similar issues before
\cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

@@

Intersections check for collisions by verifying no two agents are simultaneously
performing conflicting turns. AORTA has a low-granularity model of turn
conflict. If two vehicles at any point along two different turns could ever come
into contact, then the turns are always in conflict, no matter where the agents
actually are along that turn. This is visualized in Fig. \ref{fig:conflicts}.
Further work is required before higher granularity can be introduced through
space-time tiling intersections \cite{JAIR08-dresner}, due to some of the
complex intersection geometries inferred from OSM. An example of such a complex
intersection is shown in Fig. \ref{fig:crazyIntersection}.

@@

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads while the
simulation is running, since tasks may finish and agents may enter the road at
different times}. After setting up a scenario in the UI, users can save this
configuration for re-simulation.

>>>>

Like any other microscopic traffic simulator, AORTA needs maps to run
simulations. One of AORTA's key features is that it generates maps using real
road data available from OpenStreetMap (OSM) \cite{osm}, a moderated,
user-editable interface for world maps. A map for any desired city in the world
can be downloaded, which is then parsed by AORTA to set up a scale simulation of
the real world in a few minutes. AORTA is available open-source and is easily
extensible,\footnote{Code available at
\texttt{http://code.google.com/p/road-rage}} making it easy for users to test
out a number of agent behaviors and intersection policies in a short time span.

@@

AORTA's implementation uses Scala, a language implemented on the Java Virtual
Machine \cite{scala}. Scala provides the advantage of functional programming
constructs while still permitting imperative style.  Extensions and clients
built on top of AORTA can be written in either Java or Scala. The software is
open-source and easily extensible. For instance, the stop sign policy used
in experiments described in Section \ref{sec:results} is implemented in just 70
lines of code.

@@

The map also has a geometric interpretation, used for visualization and
measuring physical distances. A road contains a sequence of points, defining the
center line that divides the road into two directions of travel. AORTA
interprets these points as straight line segments and projects parallel lanes
out using a fixed width. Turns are approximated with a single straight line
segment connecting the end of one lane to the start of another.

@@

AORTA's map construction process, although flexible, cannot completely account
for incompleteness in OSM data. Road type annotations imprecisely imply the
number of lanes and typical speed limits. Heuristically enumerating the turns at
each intersection often misses common features like right turn-only lanes and
shared center left turn lanes. In some circumstances, one intersection appears
to be several in close proximity, since OSM has only geometric data, as opposed
to functional data, on how roads meet. If OSM encoded functional information,
the realism of the simulation would improve. Other simulators have dealt with
similar issues \cite{Krajzewicz_Hertkorn_Ringel_Wagner_2005}.

@@

Intersections check for collisions by verifying no two agents are simultaneously
performing conflicting turns. AORTA has a low-granularity model of turn
conflict. If two vehicles at any point along two different turns could ever come
into contact, then the turns are always in conflict, regardless of where the agents
actually are along the turns. This is visualized in Fig. \ref{fig:conflicts}.
Further work is required before higher granularity can be introduced through
space-time tiling intersections \cite{JAIR08-dresner}, due to some of the
complex intersection geometries inferred from OSM. An example of such a complex
intersection is shown in Fig. \ref{fig:crazyIntersection}.

@@

These experiments are deterministically reproducible. A seed for the
pseudo-random number generator, the input graph, and the generators'
configuration fully determine the outcome of any simulation \footnote{This
determinism may break down when generators use worker threads while the
simulation is running, since tasks may finish and agents may enter the road at
different times.}. After setting up a scenario in the UI, users can save this
configuration for re-simulation.
